Differentially Private Bayesian Inference

### 2018-05-01 main.tex
fix mistakes

In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$. The $m$ side dice change into a irregular coin with side $1$ and side $2$. The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $1$ in the observed data set and $n_0$ is the appearance time of the other side.

\section{Algorithm Setting up}
\label{sec_setup}
For now, we already have a prior distribution $prior$, an observed data set $x$.

@@

In exponential mechanism, candidate set $R$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
\begin{equation*}
R = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
\end{equation*}

Hellinger distance $\hlg$ is used here to score these candidates. The utility function:
\begin{equation}
\label{equ_utility}
u(x,r) = -\hlg(\bysinfer(x), r); r \in R.
\end{equation}

Exponential mechanism with global sensitivity selects and outputs a candidate $r \in R$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
\end{equation*}
where global sensitivity is calculated by:
\begin{equation*}
\Delta_{g}u = 
\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}
|\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|
\end{equation*}

@@

\subsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity share the same candidate set and utility function as it with global sensitivity. This outputs a candidate $r \in R$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u})},
\end{equation*}

@@

\begin{equation*}
\Delta_{l}u(x) = 
\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|
\end{equation*}

@@

\begin{equation*}
\underset{r \thicksim \hexpmech(x)}{Pr}[u(r) = z]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r) = e^{\lambda} z] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.
\end{lem}

@@

The sensitivity is always greater than 0, and we are using $-\hlg(\bysinfer(x),r)$ for utility function, i.e., $u(r) \leq 0$, we need to consider two cases that $\lambda < 0$, and $\lambda > 0$:

We set the $h(z) = Pr[u(\hexpmech(x)) = z] = \frac{exp(\frac{\epsilon z}{2 S(x)})}{NL_x}$.

>>>>

In the case that $m = 2$, it is reduced to a Beta distribution $\betad(\alpha, \beta)$. The $m$ side dice change into a irregular coin with side $A$ and side $B$. The posterior is computed as $(\alpha + n_1, \beta + n_0)$, where $n_1$ is the appearance time of side $A$ in the observed data set and $n_0$ is the appearance time of the other side.

\section{Algorithm Setting up}
\label{sec_setup}
For now, we already have a prior distribution $\pi(\xis)$, an observed data set $x$.

@@

In exponential mechanism, candidate set $\mathcal{R}$ can be obtained by enumerating $y \in \mathcal{X}^n$, i.e.
\begin{equation*}
\mathcal{R} = \{\bysinfer(y)\ |\ y \in \mathcal{X}^n\}.
\end{equation*}

Hellinger distance $\hlg$ is used here to score these candidates. The utility function:
\begin{equation}
\label{equ_utility}
u(x,r) = -\hlg(\bysinfer(x), r); r \in \mathcal{R}.
\end{equation}

Exponential mechanism with global sensitivity selects and outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
\end{equation*}
where global sensitivity is calculated by:
\begin{equation*}
\Delta_{g}u = 
\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|
\end{equation*}

@@

\subsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity share the same candidate set and utility function as it with global sensitivity. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u})},
\end{equation*}

@@

\begin{equation*}
\Delta_{l}u(x) = 
\max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}.
\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|
\end{equation*}

@@

\begin{equation*}
\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = z]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = e^{\lambda} z] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.
\end{lem}

@@

The sensitivity is always greater than 0, and our utility function $-\hlg(\bysinfer(x),r)$ is smaller than zero, i.e., $u(r,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

We set the $h(z) = Pr[u(\hexpmech(x)) = z] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL_x}$.
